%%% 1.3 QUALITY OF TRAINING %%%
\subsection{Quality of supervision, training, and knowledge transfer}
\label{sec:training}
% \inline{Add some words about Primož}

%The profile of the supervisor is naturally complementary to mine within our proposed research.
During the MCS fellowship in Ljubljana, I will be supervised by prof.\ Primož Potočnik. 
He is a leading expert in the area of algebraic graph theory. His work includes purely graph theoretical
results, applications of group theory in algebraic graph theory, as well as computational aspects in group theory and discrete mathematics.
He has proved a number of deep theoretical results as well as developed many new computational approaches that enabled him (and his coworkers Pablo Spiga, Gabriel Verret) to significantly increase the scope of existing datasets of highly symmetric graphs. His achievements include the census of all
cubic vertex-transitive graphs of order up to $1280$, the census of all tetravalent arc-transitive graphs of order up to $640$, the census of all
rotary maps on at most 1.500 edges etc. These datasets are one of the most used and cited resources in algebraic graph theory.

Prof.\ Potočnik has successfully supervised three PhD students (Gabriel Verret, Katja Berčič, Micael Toledo), currently supervises
a postdoctoral fellow Alejandra Ramos and has informally advised several junior members of the department.
He is the leader
of a long-term research programme funded by the Slovenian Research Agency (ARRS) and has held numerous leadership positions
(such as the Head of Department, Vice Dean of the faculty and the head of the PhD programme in mathematics).
 He has strong research ties with a number of leading research groups in discrete mathematics (such as the groups at University of Auckland, University of Ottawa, Comenius University in Bratislava, Univerist\'a degli Studi Milano etc) and regularly hosts top researchers in the area.

My joint research with prof.\ Potočnik will be supplemented by the training at the {\em mathematical knowledge management group} led by Katja Berčič.
Dr.\ Berčič has recently returned from her postdoctoral training at the KWARC group at FAU in Erlangen, led by
prof.\ Michael Kohlhase. She is now actively involved in a development of MathDataHub, a semantic portal that provides a web interface to datasets. The interface supports easy filtering, searching and customisable presentation of individual objects.


I will also regularly interact and discuss different aspect of my research with other members of a very strong discrete mathematics and theoretical computer science group at the University of Ljubljana, which includes high profile researchers, such as prof.\ Bojan Mohar (jointly appointed with Simon Fraser University, Canada), prof.\ Sandi Klavžar, prof.\ Riste Škrekovski, prof.\ Tomaž Pisanski, prof.\ Andrej Bauer etc. Having an opportunity to regularly meet and work with researchers of this level will contribute significantly to my professional growth.

Finally, a board of external advisors will be formed, consisting of top experts in the relevant areas of mathematics (including prof.\ Marston Conder, prof. Pablo Spiga, prof. Asia I. Weiss and prof. Gabe Cunningham and prof. Isabel Hubard, ), who will regularly check on the progress of my research and advise on further directions.




Working under the supervision of prof. Potočnik a MSCA fellow, I hope to draw from his vast experience on theoretical and computational issues in algebraic graph theory. In particular, I hope acquire several new skills, including:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item ability of using advanced group theoretical methods relevant for the topic of the proposed research;
\item proficiency in development of software packages (\gap, \sage\ , \magma) for discrete mathematics;
\item internet programming skills, such as construction of user-friendly internet platforms;
\item understanding mathematical knowledge management (presenting and storing mathematical data under FAIR principles).
\end{itemize}

My training  will consists of:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item daily short research meetings with the supervisor (at least 4 times a week),
where progress on the project and obstacles and possible solutions will be discussed;
\item longer research sessions with the supervisor (once to twice per week);
\item weekly meetings with the knowledge management group at the department (led by dr.\ Katja Berčič),
where
\item attending the meetings of the discrete mathematics group at the department (once a week) and research sessions with individual members of
the group (based on the specific needs of the project)
\item  intensive research retreats (in duration of at least 5 days at least once per 2 months) where meetings with the advisory board will be organised.
\end{itemize}




% **

% While developing the proposed research I will receive training on two different  \emph{theoretical skills} that have been previously used to build datasets of graphs.
% We shall explore if and how they could be adapted to developing datasets of polytopes.
% On the other hand, to develop the computational part of the project I will acquire new skills on developing and managing datasets.
% This skills includes \emph{development of software packages} (\gap, \sage\ , \magma), \emph{database management} (SQL)  and \emph{data publishing} (FAIR repositories, website building, CVS-files manipulation).
% \todo{Improve this paragraph}
On the other hand,
my experience on the topic subject of abstract polytopes 
complements the more graph- and group-theoretical expertise of
the supervisor and the discrete mathematical group at the host institution.
The complementary nature of the expertise of the supervisor and myself
will have synergetic effects needed to fulfil the objectives of \ourp.

%with expertise on problems related to building abstract polytopes and similar objects with prescribed combinatorial constraints or imposed symmetry conditions.
%FMF-UL is already a leading institution on discrete mathematics and some successful researchers on abstract polytopes and related objects have been formed in this institution in the past.
%However, there is no currently an active researcher working on this topic.
%My presence in FMF-UL will serve as fists steps to revive the area in an already strong environment on discrete mathematics.


% At a minimum, address the following aspects:

%     • Describe the qualifications and experience of the supervisor(s). Provide information regarding the supervisors' level of experience on the research topic proposed and their track record of work, including main international collaborations, as well as the level of experience in supervising/training, especially at advanced level (i.e. PhD and postdoctoral researchers).
%     • Planned training activities for the researcher (scientific aspects, management/organisation, horizontal and key transferrable skills...).
%     • For European Fellowships: two-way transfer of knowledge between the researcher and host organisation.
%     • For Global Fellowships: three-way transfer of knowledge between the researcher, host organisation, and associated partner for outgoing phase.
%     • Rationale and added-value of the non-academic placement (if applicable).
%
% Supervision
% Employers and/or funders should ensure that a person is clearly identified to whom researchers can refer for the performance of their professional duties, and should inform the researchers accordingly.
% Such arrangements should clearly define that the proposed supervisors are sufficiently expert in supervising research, have the time, knowledge, experience, expertise and commitment to be able to offer the research doctoral candidate appropriate support and provide for the necessary progress and review procedures, as well as the necessary feedback mechanisms.
%
%  Supervision is one of the crucial elements of successful research. Guiding, supporting, directing, advising and mentoring are key factors for a researcher to pursue his/her career path. In this context, all MSCA-funded projects are encouraged to follow the recommendations outlined in the MSCA Guidelines on Supervision.


%%% 1.3.1 SUPERVISOR %%%
% \marginLeft{Supervisor}%
% Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
%
%
% %%% 1.3.2 GROUP %%%
% \colorrule
% \marginLeft{Group}%
% Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?
%
% %%% 1.3.3 KNOWLEDGE TRANSFER %%%
% \colorrule
% \marginLeft{Knowledge transfer}%
% At vero eos et accusamus et iusto odio dignissimos ducimus qui blanditiis praesentium voluptatum deleniti atque corrupti quos dolores et quas molestias excepturi sint occaecati cupiditate non provident, similique sunt in culpa qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Et harum quidem rerum facilis est et expedita distinctio. Nam libero tempore, cum soluta nobis est eligendi optio cumque nihil impedit quo minus id quod maxime placeat facere possimus, omnis voluptas assumenda est, omnis dolor repellendus.
%
% Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet ut et voluptates repudiandae sint et molestiae non recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.
% \textsl{Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.}
%
%
%
