%%% 2.2 QUALITY OF PROPOSED MEASURES %%%
%Suitability and quality of the measures to maximise expected outcomes and impacts, as set out in the dissemination and exploitation plan, including communication activities
\subsection{Suitability and quality of the measures to maximise expected outcomes and impacts, as set out in the dissemination and exploitation plan, including communication activities}
\label{sec:suitability}

% \color{magenta}
% Write this in parallel with RO4. Whatever we promise there, it should mentioned here.
% Aslo mention that the people at KWARC are very interested in finding people that construct datasets in mathematics, so they are natural users of our project.
% \color{black}


Our proposed research sits on the interplay of computer science and theoretical mathematics.
However, as most basic research the end users will be other researchers working on symmetries of discrete objects.
We should emphasise that our overall goal is to improve the way research on this area is performed.

Our plan of dissemination can be divided into two main categories: local audience and international audience.

For the local audience I will continuously participate on with talks on the seminar of Discrete Mathematics of the host institution (FMF-UL) as well as the seminar of Combinatorics and group theory of the Faculty of education of the University of Ljubljana (PeF-UL).
Those two seminars will allow me to constantly disseminate my research among the local researchers.
Those researchers can will test the quality and efficiency of the built datasets and will offer constant feedback.

For the international audience we should publish research articles in open access journals that show the potential of our research.
Meaning that we should not only write and publish articles that explain how we build datasets of polytopes but we should serve as the firsts users of these datasets.
We should direct our theoretical research towards the use of these datasets to show the potential they have to improve the way basic research is performed.

I will participate in international conferences to present and disseminate our research. I will present the first advances of our research in a talk in the International Slovenian Conference on Graph theory, which is an international forum that occurs every 4 years and has had more than 300 participants in the last editions.

In order to optimize the development of the computational part of our project, I shall organise at least one programming workshop per year were both researchers and students will get together and discuss problems regarding datasets of discrete objects.
This will also serve to get users that will test our developed datasets.

Finally, I shall visit at least once a year a member of the external advisory committee in order to adapt the development of our research to the needs of the community.

On the other hand, our project will be a case of study of the KWARC group.
They not only be beneficiated from the final research products but also from the process of developing these datasets as part of their research on mathematical knowledge management.
We shall measure this impact by having constant meetings with Dr. Berčič, who participates in this group, but also by invinting active research on mathematical knowlege managemente to orient, supervise and participate on the organised workshops.


%
% At a minimum, address the following aspects:
% Plan for the dissemination and exploitation activities, including communication activities:1 Describe the planned measures to maximize the impact of your project by providing a first version of your ‘plan for the dissemination and exploitation including communication activities’. Describe the dissemination, exploitation measures that are planned, and the target group(s) addressed (e.g. scientific community, end users, financial actors, public at large). Regarding communication measures and public engagement strategy, the aim is to inform and reach out to society and show the
% activities performed, and the use and the benefits the project will have for citizens. Activities must be strategically planned, with clear objectives, start at the outset and continue through the lifetime of the project. The description of the communication activities needs to state the main messages as well as the tools and channels that will be used to reach out to each of the chosen target groups.
%     • Strategy for the management of intellectual property, foreseen protection measures: if relevant, discuss the strategy for the management of intellectual property, foreseen protection measures, such as patents, design rights, copyright, trade secrets, etc., and how these would be used to support exploitation.
%
%     • All measures should be proportionate to the scale of the project, and should contain concrete actions to be implemented both during and after the end of the project.



%%% 2.2.1 DISSEMINATION %%%
% \colorrule
% \marginLeft{Dissemination}%
% Sed ut perspiciatis unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam, eaque ipsa quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt explicabo. Nemo enim ipsam voluptatem quia voluptas sit aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos qui ratione voluptatem sequi nesciunt. Neque porro quisquam est, qui dolorem ipsum quia dolor sit amet, consectetur, adipisci velit, sed quia non numquam eius modi tempora incidunt ut labore et dolore magnam aliquam quaerat voluptatem. Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Quis autem vel eum iure reprehenderit qui in ea voluptate velit esse quam nihil molestiae consequatur, vel illum qui dolorem eum fugiat quo voluptas nulla pariatur?
%
% %%% 2.2.2 COMMUNICATION %%%
% \colorrule
% \marginLeft{Communication}%
%
%
%
% %%% 2.2.3 STRATEGY %%%
% \colorrule
% \marginLeft{Strategy}%
